---
title: "Intro to R - 2"
author: "Arun kr. Khattri"
date: "Sep 27, 2019"
output:
  html_document:
    fg_height: 5
    fig_width: 8
    highlight: tango
    number_sections: no
    theme: cerulean
    toc: yes
---
<style type = "text/css">
body{ /* Normal */
  font-size: 14px;
}
h1{ /* Header 1 */
  font-size: 24px;
}
h2{ /* Header 2 */
  font-size: 20px;
}
h3{ /* Header 3 */
  font-size: 16px;
}
code.r{ /* Code Block */
  font-size: 12px;
}
pre{ /* Code Block */
  font-size: 12px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries required

```{r message=FALSE}
library(tidyverse)
library(openintro)
```

## Sampling
### load county data
```{r}
data(county)
glimpse(county)
```

### unique values

```{r}
unique(county$state)
```

### length of unique values

```{r}
length(unique(county$state))
```

### unique values in county data

```{r}
sapply(county, function(x) length(unique(x)))
```

## remove "District of Columbia" as technically its not a state

```{r}
county_noDC <- county %>% 
  filter(state != "District of Columbia") %>% 
  droplevels()

# check unique values in data set
sapply(county_noDC, function(x) length(unique(x)))
```

## simple random sample of 150 counties

```{r}
county_srs <- county_noDC %>% 
  sample_n(size = 150)

glimpse(county_srs)
```

### State distribution of srs counties

```{r}
county_srs %>% 
  group_by(state) %>% 
  count()
```

## Stratified Sampling

```{r}
county_str <- county_noDC %>% 
  group_by(state) %>% 
  sample_n(size = 3)

# State distribution of str counties
county_str %>% 
  group_by(state) %>% 
  count()
```

## Principles of Experimental design
* Control: compare treatment of interest to a control group
* Randomize: randomly assign subjects to treatments
* Replicate: collect a sufficiently large sample within a study, or replicate the entire study.
* Block: account for the potential effect of confounding varables
  + group subjects into blocks based on these variables.
  + Randomize within each block to treatment groups

